Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-07-03 related.tex
Modificacion 1 parte related works

Several efforts have been made to apply machine learning techniques in
the automated discovery of relationships between environmental
variables and quantified descriptors for variables of agricultural 
interest such as the progress of diseases.
% 
\citet{Huang2010} summarize in their survey the
development of soft computing techniques in agricultural and
biological engineering, including fuzzy logic, artificial neural
networks, genetic algorithms, bayesian inference and decision trees.
%
Similarly, \citet{Kim2014} survey more recent prediction
methods for crop pests using regression and machine learning approaches.

\TODO{Falta indicar qué concluyen los dos surveys anteriores}

>>>>

Several efforts have been made to apply machine learning techniques in
the automated discovery of relationships between environmental
variables and quantified descriptors for variables of agricultural 
interest such as the progress of diseases.
% 
\citet{Huang2010} summarize in their survey the
development of soft computing techniques in agricultural and
biological engineering, especially in the soil and water context for crop management and decision support in precision agriculture, including fuzzy logic, artificial neural
networks, genetic algorithms, Bayesian inference and decision trees. They do not present numeric results of each paper, only mention the main idea.
%
Similarly, \citet{Kim2014} survey more recent prediction
methods for crop pests using regression and machine learning approaches. Nor do they provide numerical results of each paper.

\TODO{Falta indicar qué concluyen los dos surveys anteriores - Modificado: como indico, en realidad ellos mencionan qué métodos han usado en los paper, pero no dan R2 o rmse, ni detallan resultados en general}
